### 2008-05-16 trunk/Papers/dl-gre-08/gre.tex
fits on 8 pages; finished as far as I am concerned

We will now see what our algorithms do for some interesting
examples. Consider the model shown in Fig.~\ref{fig:dale-haddock}a,
which is taken from \newcite{dale91:_gener_refer_expres_invol_relat},
and let's run the $\el$ algorithm.

The algorithm starts with $\RE = \{\top\}$.  In the first loop, it
adds the formulas $\mathsf{floor}$, $\mathsf{bowl}$, $\mathsf{cup}$,
and $\mathsf{table}$, and then removes $\top$ because it is now
subsumed.  Not all of these formulas denote singletons; for instance,
$\interp{\mathsf{cup}}$ contains two individuals.  So we iterate over
the relations to refine our formulas.  After the first iteration over
the relations, we have $\RE = \{ \mathsf{floor}, \mathsf{bowl} \sqcap
\exists \mathsf{on}.\mathsf{floor}, \mathsf{bowl} \sqcap \exists
\mathsf{on}.\mathsf{table}, \mathsf{cup}, \mathsf{table} \}$. Notice
that $\mathsf{bowl}$ has become subsumed, but we haven't distinguished
the cups and tables further.

>>>>

Let's try our algorithms on some examples.  We first run the \el\
algorithm on the model shown in Fig.~\ref{fig:dale-haddock}a, which is
taken from \newcite{dale91:_gener_refer_expres_invol_relat}.  The
algorithm starts with $\RE = \{\top\}$.  In the first loop, it adds
the formulas $\mathsf{floor}$, $\mathsf{bowl}$, $\mathsf{cup}$, and
$\mathsf{table}$, and then removes $\top$ because it is now subsumed.
Not all of these formulas denote singletons; for instance,
$\interp{\mathsf{cup}}$ contains two individuals.  So we iterate over
the relations to refine our formulas.  After the first iteration over
the relations, we have $\RE = \{ \mathsf{floor}, \mathsf{bowl} \sqcap
\exists \mathsf{on}.\mathsf{floor}, \mathsf{bowl} \sqcap \exists
\mathsf{on}.\mathsf{table}, \mathsf{cup}, \mathsf{table} \}$. Notice
that $\mathsf{bowl}$ has become subsumed, but we haven't distinguished
the cups and tables further.
